\documentclass[a4paper,10pt]{article}

% TODO:
% - Needs more deep learning. Add the Yamins project and the State Estimation project to beef up DL.
% 

%A Few Useful Packages
\usepackage{tabularx}
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
%usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage[cm]{fullpage}
%Setup hyperref package, and colours for links

\usepackage[margin=0.2in,bottom=0.1in, top=0.25in]{geometry}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\usepackage{hyperref}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
%\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\raggedright\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}


%---------publications
\renewcommand\refname{Publications}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
{\centering
		{\Large Ram\'{o}n Dar\'{i}o   Iglesias
	}\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data
%\section{Contact Information}

\centering{650.669.7306 | \href{mailto:rdit@stanford.edu}{rdit@stanford.edu} | \url{http://ramondario.com}}

%Section: Interests
%\section{Research Interests}
%\begin{tabularx}{\textwidth}{lX}
%Machine Learning, Artificial Intelligence, Reinforcement Learning, Representation Learning, Optimization %\\

%\bf{Theory:}& Machine Learning, Representation Learning, Deep Learning\\ \\ 
%\end{tabularx}

%Section: Work Experience at the top
\section{Recent Experience}
\begin{tabularx}{\textwidth}{Xr}

 {\bf{Lyft Inc.}}, San Francisco, CA & \bf{09/2019-Present}\\
 \emph{Research Scientist} &\\
 \multicolumn{2}{p{0.98\textwidth}}{
 Working on driver positioning algorithms:
 \begin{itemize}
 	\item Positional signals for drivers to improve their earnings.
 \end{itemize}
 }\\

 {\bf{Stanford University}}, Stanford, CA & \bf{01/2016-08/2019}\\
 \emph{Research Assistant} &\\
 \multicolumn{2}{p{0.98\textwidth}}{
 Devising methods to model and control large fleets of autonomous vehicles (Autonomous Mobility-on-Demand, or AMoD):
 \begin{itemize}
 	\item Developed a queueing-theoretical framework to characterize AMoD systems under heterogeneous constraints (e.g. road congestion, battery charging) that is amenable to optimization by casting it as a linear program \cite{IglesiasRossiEtAl2016,IglesiasRossiEtAl2017}.
 	\item Leveraged network flow theory to optimize the interaction between autonomous, electric fleets and the power grid \cite{RossiIglesiasEtAl2018,RossiIglesiasEtAl2018b}.
 	\item Devised and trained recurrent neural networks to predict short-term travel demand and developed a stochastic model predictive controller that leverages these forecasts to operate in real-time large fleets of autonomous vehicles \cite{IglesiasRossiEtAl2018,TsaoIglesiasEtAl}.
 	\item Collaborated with Toyota to implement vehicle relocation algorithms in their carsharing system, Ha:mo, in Japan. Developed a web application (React frontend, Python backend) that allows human operators to visualize the current and forecasted state of the system as well as receive rebalancing tasks that optimize for vehicle availability.
 \end{itemize}
 Side projects in representation learning:
 \begin{itemize}
 	\item Investigated the impact of multi-task learning on the learned representations of convolutional neural networks. Results show increased predictive power with respect to representations observed in the Inferior Temporal (IT) cortex of primates.
 	\item Developing deep learning methods to learn embedded, controllable representations of nonlinear systems from high-dimensional observations. 
 \end{itemize}
 }\\
 %\multicolumn{2}{c}{} \\

 {\bf{Lyft Inc.}}, San Francisco, CA & \bf{06/2018-09/2018}\\
 \emph{Research Science Intern} &\\
 \multicolumn{2}{p{0.98\textwidth}}{
 Worked on improving the performance of Lyft's self-driving pilot:
 \begin{itemize}
 	\item Developed an algorithm that leverages demand forecasts and stochastic programming to optimize self-driving fleet movements in real-time. Simulation results show significant improvements in pickup time when compared to human drivers.
 	\item Performed steady-state analyses to characterize upper bound (using network flows) and expected improvements (using queueing theory) based on historical data. This along with power analyses allowed us to design experiments in production.
 	\item Deployed the prepositioning algorithm to a self-driving pilot in Las Vegas as part of an A/B test to understand the impact of prepositioning in ridesharing fleets.%prod
 \end{itemize}
 }\\
 %\multicolumn{2}{c}{} \\

{\bf{SunPower}}, Richmond, CA & \bf{01/2015-01/2016}\\
\emph{Software Engineer} &\\
\multicolumn{2}{p{0.98\textwidth}}{
Architected and developed software for the Financial Products team:
\begin{itemize}
	\item Built a new pricing engine (Python backend), reducing the cost by 80\% and the response time by 90\%.
	\item Developed an internal data processing web application to run and visualize complex financial analyses (Python backend, Angular frontend).
	\item Built the continuous integration pipeline (Docker, Salt, git) for the Financial Products team allowing for faster and safer developing iterations.
\end{itemize}
}\\
%\multicolumn{2}{X}{} \\

{\bf{Stanford University}}, Stanford, CA & \bf{10/2013-12/2014}\\
\emph{Research Assistant} &\\
\multicolumn{2}{p{0.98\textwidth}}{
Developed methods to optimize wind farm contractors operational costs:
\begin{itemize} 
	\item Built Markov chain models to forecast the expected number of days lost due to high winds by month and the best hours of the day to work each month using historical wind speed measurements and numerical weather prediction models.
	\item Developed a data processing and optimization pipeline for converting GIS files of wind farms into optimal erection schedules. It consists of parsing the input files into a weighted graph and solving the crane schedule as a Traveling Salesman Problem. 
	\item Built a web application (Angular frontend, Python backend) for wind farm contractors to leverage the wind forecasting and crane scheduling models to make better decisions on the design and construction schedule of the wind farm.
\end{itemize}
}\\
%\multicolumn{2}{c}{} \\

% \bf{06/2013-08/2013} &  \bf{Project Frog}, San Francisco, CA \\&\emph{Inventory Control Intern}\\&\footnotesize{Coordinated building component deliveries and tracked material inventories for four different school construction sites totaling 17 buildings within a three month schedule.}\\\multicolumn{2}{c}{} \\

%\bf{06/2012-08/2012} &  \bf{Steger Bizzell}, Georgetown, TX \\&\emph{Water Utility Modeling Intern}\\&\footnotesize{Modeled a utility company's water and wastewater infrastructure using ArcGIS to provide asset management, demand forecast, and network optimization.}\\\multicolumn{2}{c}{} \\

%\bf{07/2011-08/2011} &  \bf{Consorcio Carlo}, Guadalajara, Mexico \\&\emph{Superintendent}\\&\footnotesize{Developed the schedule, procured the required materials, managed the on-site operations, and helped prepare permit applications for a small residential project}\\\multicolumn{2}{c}{} \\

%\bf{06/2011-07/2011} &  \bf{Grupo Atelier}, Guadalajara, Mexico \\&\emph{Cost Estimating Intern}\\&\footnotesize{Prepared detailed cost estimates for a range of different house designs of a residential development.}\\\multicolumn{2}{c}{} \\

%\end{tabularx}

%Section: Research
%\section{Research Experience}
%\begin{tabularx}{\textwidth}{Xr}

%\bf{Stanford University} & \bf{10/2013-05/2014}\\
%\emph{Wind Farm Layout Optimization} &
%\\\multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{\footnotesize{
%	Reduced wind farm construction costs by 6\% by developing, as part of a multidisciplinary team, a method to parametrize construction cost, and optimize wind turbine layout and construction schedule. 
%}}
%\\
%\multicolumn{2}{c}{} \\

%\bf{09/2010-05/2011} &  \bf{The University of Texas at Austin}\\&\emph{Life-Cycle Analysis using Building Information Models}\\&\footnotesize{Mapped the workflow and information dependency for building life-cycle costing and energy modeling through industry case studies. Developed a framework based on Building Information Modeling to improve the process.}\\\multicolumn{2}{c}{} \\

%\bf{11/2009-07/2010} &  \bf{Technical University Munich}\\&\emph{High Performance Concrete Adhesives}\\&\footnotesize{Tested different concrete adhesive when applied to high performance concrete.}\\\multicolumn{2}{c}{} \\

\end{tabularx}

%Section: Education
\section{Education}

\begin{tabularx}{\textwidth}{Xr}	
 \bf{Stanford University} & \bf{01/2016-08/2019}\\ 
\emph{Ph.D. in Civil Engineering}&\\
\multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{Advisor: Marco Pavone}\\
\multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{Focus: Optimal Control of Autonomous Fleets.}\\
\\%\multicolumn{2}{c}{} \\

 \bf{Stanford University} & \bf{09/2012-06/2014} \\ 
\emph{M.S. in Civil Engineering} &
\\\multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{Focus: Data Analysis and Optimization.}\\
\\
%\multicolumn{2}{c}{} \\

\bf{The University of Texas at Austin} & \bf{08/2007-06/2012}\\
\emph{B.S. in Civil Engineering} &\\
%\multicolumn{2}{c}{} \\
\end{tabularx}


%Section: Scholarships and additional info
%\section{Selected Projects}
%\begin{tabularx}{\textwidth}{Xr}

% \bf{groupstats.io} & \bf{08/2015-12/2015} \\
% \emph{Side Project} &\\
% \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{\footnotesize{Designed the architecture, and built frontend and backend features for  \emph{groupstats.io}, a web application that allows users to visually analyze the dynamics of their Whatsapp chats.}}\\
% \multicolumn{2}{c}{} \\

%\bf{Let's Get Weird} & \bf{11/2014-01/2015}\\
%\emph{Startup Weekend} &\\
%\multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{\footnotesize{Built a mobile app to share pictures with nearby people during the peak nightlife hours.}}\\
%\multicolumn{2}{c}{} \\

 %\bf{Industrialized Construction Studio} & \bf{09/2013-04/2014}\\
 %\emph{Stanford University} &\\
 %\multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{\footnotesize{Helped organized a course investigating the methods, drivers and barriers of industrialized construction through engagement with American and Swedish companies in the form of site visits, lectures, and joint projects.}}\\
 %\multicolumn{2}{c}{} \\

%\bf{11/2013- 12/2013} &  \bf{Stanford University}\\&\emph{Learning Algorithm for Optimization}\\&\footnotesize{Developed a Naive Bayes based algorithm to accelerate the optimization of Wind Farm Layouts}\\\multicolumn{2}{c}{} \\

%\bf{03/2011-05/2012} &  \bf{The University of Texas at Austin}\\&\emph{Modular Steel Frame Optimization}\\&\footnotesize{Developed a model that optimized the spatial arrangement and sizing arrangement of a steel frame modular building.}\\\multicolumn{2}{c}{} \\

%\bf{04/2010-08/2010} &  \bf{Technical University Munich}\\&\emph{Risk Based Flood Protection Optimization}\\&\footnotesize{Optimized a flood protection system by balancing the trade-off between mitigation cost and expected cost of failure under different land use scenarios.}\\\multicolumn{2}{c}{} \\

%\end{tabularx}







%Section: Skills

\section{Skills}
\begin{tabularx}{\textwidth}{lX}
\bf{Software:}& Python (Numpy, Pandas, Tensorflow, PyTorch, Flask), Javascript (React, AngularJS, D3, Leaflet), R; AWS, Spark, Git, Docker, CircleCI, PostgreSQL, \LaTeX \\ \\ 

 \bf{Coursework:}& Machine Learning, Data Mining, Decision Making under Uncertainty, Optimization, Deep Learning, Data Visualization, Optimal Control, State Estimation, Web Development\\ \\ 

 %\bf{Sports:}& Show Jumping, Soccer, Racquetball\\ \\

 %\bf{Languages:}& Spanish (native), English (fluent), German (intermediate)\\ \\ 
\end{tabularx}

\nocite{*}
\bibliographystyle{habbrvyr}
\bibliography{../bib/iglesias}

\end{document}
